Towards Contract Modules for the Tezos Blockchain

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
conclusion

Current blockchains often provide low-level interfaces to interact with smart contracts. These interfaces work with loosely structured data that is impractical for programs to handle. This paper presents outgoing research on programmatic interaction with a smart contract on the Tezos blockchain that could benefit developers of smart contract applications and Oracles. The approach does not provide a general API, but targets each typical smart contract by generating a specialized contract module that provides a typed high-level interface from a smart contract implementation. In doing so, errors in contract calls are explicitly specified in a user-defined data type. A contract call is treated as a function call that grants a typed safe of data in the Ocaml language. In addition, the module can check preconditions before the actual call to reduce the waste of a failed call. As future work, we combine the contract module with our typed API designed to provide a general type-safe programmatic API for the Tezos blockchain.

>>>>

Current blockchains often provide low-level interfaces to interact
with smart contracts. These interfaces work with loosely structured
without static guarantees. This paper presents ongoing research on the
programmatic interaction with smart contracts on the Tezos blockchain
that could benefit developers of mixed applications and
oracles comprised of on-chain and off-chain parts. The approach does
not provide a general API, but targets each 
individual smart contract by generating a specialized contract module
that provides a typed high-level interface from a contract
specification. In doing so, errors from contract calls are explicitly
specified in a user-defined data type. A contract call is wrapped in a
fully typed and integrated OCaml function. In addition, the wrapper can check preconditions before the 
actual call to reduce the waste of gas of a failed call.
% As future work, we
% combine the contract module with our typed API designed to provide a
% general type-safe programmatic API for the Tezos blockchain.
